Parsing Postfix log files

### 2008-03-10 doc/logparser.tex
Update the number of rules.
Corrected reference to pid_regex.

\newcommand{\numberOFrules}[0]{%
    168%
}

@@

    \item [result\_cols, connection\_cols] Specifies how the fields in the
        log line will be extracted from the log line.  The format is:
        \newline \texttt{smtp\_code = 1; recipient = 2, sender = 4;}
        \newline i.e.\ semi-colon or comma separated assignment statements,
        with the variable name on the left and the matching capture from
        the \regex{} on the right hand side.  The list of acceptable
        variable names is:

@@

        Additionally \texttt{pid\_regex} and \texttt{child} are used by the
        \texttt{TRACK, BOUNCE} and \texttt{SMTPD\_DIED} actions.

>>>>

\newcommand{\numberOFrules}[0]{%
    161%
}

@@

    \item [result\_cols, connection\_cols] Specifies how the fields in the
        log line will be extracted.  The format is:
        \newline \tab{} \texttt{smtp\_code = 1; recipient = 2, sender = 4;}
        \newline i.e.\ semi-colon or comma separated assignment statements,
        with the variable name on the left and the matching capture from
        the \regex{} on the right hand side.  The list of acceptable
        variable names is:

@@

        Additionally \texttt{child} and \texttt{pid} are used respectively
        by the \texttt{TRACK}, \texttt{BOUNCE} and \texttt{SMTPD\_DIED}
        actions.
